Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2017-08-09 geometry.tex
Shorter axis
geometry figure: bigger text

  \begin{scope}[transform canvas={rotate={4}}]
    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.4};
    \path (3.33, 0) node[above,orange!80!black] {Raman F2};
    \path (2.9, 0) node[below,orange!80!black] {\textbf{(R3)}};
  \end{scope}
  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:0.3);
  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:-0.3);

@@

    \draw[blue, dotted, line width=0.5] (-4.0, 0) -- (4.0, 0);

    \fill[blue!50!black,opacity=0.1] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \draw[blue!50!black, densely dotted,line width=0.6] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.6};
    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.6};
    \arrowthreeD{cyan!40!blue}{(0.4, 0)}{-90}{0.4}{1.6};
    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.6};
    \path (1.6, 0) node[below,cyan!20!blue!80!black] {OP};
    \path (-1.25, 0) node[above,orange!80!black] {Raman F2};
    \path (-1.6, 0) node[below,orange!80!black] {\textbf{(R1)}};

    \path (0, 1.5) node[left,red!80!black,align=center] {Raman F1\\\textbf{(R2)}};

    \path (0, -1.7) node[right,red!80!black,align=center] {Raman F1\\\textbf{(R4)}};

    \draw[white,opacity=0.5,->,>=stealth,line width=1.5] (2.21, 2.39) -- (0.81, 2.39);
    \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
    \path (1.51, 2.39) node[below,white,opacity=0.5] {B field};
    \path (1.5, 2.4) node[below] {B field};

@@

  \path (-140:\theight) node[white] {\textbf{Tweezer}};
\end{tikzpicture}

>>>>

  \begin{scope}[transform canvas={rotate={4}}]
    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.4};
    \path (3.46, 0) node[above,orange!80!black] {\large Raman F2};
    \path (2.9, 0) node[below,orange!80!black] {\textbf{(R3)}};
  \end{scope}
  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:0.3);
  \draw[->,>=stealth,line width=0.8,color=black!60] (4:4.4) -- ++ (90-30:-0.3);

@@

    \draw[blue, dotted, line width=0.5] (-3.0, 0) -- (3.5, 0);

    \fill[blue!50!black,opacity=0.1] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \draw[blue!50!black, densely dotted,line width=0.6] (-2.5, 2.7) -- (2.5, 2.7)
    -- (2.5, -2.7) -- (-2.5, -2.7) -- cycle;
    \arrowthreeD{red}{(0, -0.4)}{180}{0.4}{1.6};
    \arrowthreeD{orange}{(-0.4, 0)}{90}{0.4}{1.6};
    \arrowthreeD{cyan!40!blue}{(0.4, 0)}{-90}{0.4}{1.6};
    \arrowthreeD{red}{(0, 0.4)}{0}{0.4}{1.6};
    \path (1.6, 0) node[below,cyan!20!blue!80!black] {\large OP};
    \path (-1.2, 0) node[above,orange!80!black] {\large Raman F2};
    \path (-1.6, 0) node[below,orange!80!black] {\textbf{(R1)}};

    \path (0, 1.5) node[left,red!80!black,align=center] {{\large Raman F1}\\\textbf{(R2)}};

    \path (0, -1.7) node[right,red!80!black,align=center] {{\large Raman F1}\\\textbf{(R4)}};

    \draw[white,opacity=0.5,->,>=stealth,line width=1.5] (2.21, 2.39) -- (0.81, 2.39);
    \draw[->,>=stealth,line width=1.5] (2.2, 2.4) -- (0.8, 2.4);
    \path (1.51, 2.39) node[below,white,opacity=0.5] {\large B field};
    \path (1.5, 2.4) node[below] {\large B field};

@@

  \path (-140:\theight) node[white] {\Large \textbf{Tweezer}};
\end{tikzpicture}
